An Efficient Minibatch Acceptance Test for Metropolis-Hastings

### 2016-10-12 aistats2017.tex
removing newpage before references:
Adding NIPS 2016 submission section because we need it
Added in our supplementary page regarding NIPS. I think this covers everything.

\begin{table}[t]
    \caption{Error in $X_{\rm norm}+X_{\rm corr}$ versus $X_{\rm log}$}
    \label{tab:xcorr}
    \centering
    \begin{tabular}{l l l l}
    ${\bf N}$ & ${\bf \sigma}$ & ${\bf \lambda}$ & ${\bf L_{\infty}}$ {\bf error} \\
    \hline
    4000 & 0.9 & 1 & 1.0e-4  \\
    4000 & 0.8 & 0.03 & 5.0e-6 \\
    \end{tabular}
\end{table}

@@

\newpage
\subsubsection*{References}
% Daniel: Sorry, I don't know why this is needed to get rid of the annoying
% spaces below the "References" text.
\vspace{-20pt} 
%\bibliographystyle{apalike}
\bibliographystyle{abbrvnat}
\setcitestyle{authoryear,open={[},close={]}}
\bibliography{aistats2017}

@@

>>>>

\begin{table}[t]
    \caption{Error ($L_\infty$) in $X_{\rm norm}+X_{\rm corr}$ versus $X_{\rm log}$}
    \label{tab:xcorr}
    \centering
    \begin{tabular}{l l l l}
    ${\bf N}$ & ${\bf \sigma}$ & ${\bf \lambda}$ & ${\bf L_{\infty}}$ {\bf error} \\
    \hline
    4000 & 0.9 & 1 & 1.0e-4  \\
    4000 & 0.8 & 0.03 & 5.0e-6 \\
    \end{tabular}
\end{table}

@@

%\newpage
\subsubsection*{References}
% Daniel: Sorry, I don't know why this is needed to get rid of the annoying
% spaces below the "References" text.
\vspace{-20pt} 
%\bibliographystyle{apalike}
\bibliographystyle{abbrvnat}
\setcitestyle{authoryear,open={[},close={]}}
\bibliography{aistats2017}

@@

% Daniel: don't forget this. The AISTATS website says to put it in the
% supplementary material, so I put it at the very end on a new page (to make it
% more noticeable). Obviously for the arXiv version, we don't want this there.
% Also, note to John, the reviewers for AISTATS **will have access to the
% previous NIPS reviews**, which is why I am making references to those.
\newpage
\section{NIPS 2016 Submission Statement}

We previously submitted a much older draft of this paper to NIPS 2016. The
current manuscript has been substantially revised since that submission. We have
made the following changes:

\begin{enumerate}
    \item At the time of the NIPS submission, we were unaware of several
    references which described some of what we wrote. For this submission, we
    now cite the important work of~\citep{TallData15} which had the idea of
    using subsampling noise for exploration (rather than the $\log u$ variable).
    We also cite the work of~\citep{Barker65} which uses the Barker function. We
    welcome information about other potentially missing references.

    \item The previous theoretical results have been entirely scrapped and
    replaced with different but more relevant results. The NIPS submission
    listed a page of theoretical results which did not tie into the rest of the
    paper's contributions and were confusing to the readers. We now have
    theoretical results that are much clearer and also \emph{directly} show the
    expected performance benefits of our acceptance test. Note also that
    Lemma~\ref{lem:worst_case} is an entirely new addition to this version.

    \item Several reviewers mentioned that our deconvolution approach to
    determine the correction distribution was not unique and thus ill-defined.
    Consequently, we have added an entirely new section of the paper
    (Section~\ref{sec:correction}) explaining how we derived that distribution.

    \item Reviewers pointed out one of our mistakes when we said our minibatch
    sizes were fixed. We have changed this in the current manuscript to mean
    that the per-iteration minibatch sizes for our test have a distribution with
    \emph{shorter tails} than those of prior work, which can be observed by
    plotting a histogram of minibatch sizes.

    \item Our experiments now include new comparisons with a baseline
    from~\citep{icml2014c1_bardenet14} (in addition to~\citep{cutting_mh_2014},
    which we had earlier). In addition, each algorithm now runs MCMC sampling on
    the \emph{same} distribution.  Previously, we ran our distribution at a
    higher temperature but kept the algorithm from~\citep{cutting_mh_2014}
    running on the distribution at temperature $T=1$. In this set of
    experiments, we tuned hyperparameters of the other algorithms to make the
    comparison fairer. Finally, in the Gaussian mixture model scenario
    (Section~\ref{ssec:gaussians}), we provide more details on how ``accurate''
    the samples are, rather than solely relying on the visualization of
    Figure~\ref{fig:gauss_mix_1}.

    \item We improved Algorithm~\ref{alg:our_algorithm} so that we show
    explicitly when we compute the moments, and why we now only need one
    distribution $C_\sigma$ for $\sigma=1$ due to the extra $X_{\rm nc}$
    variable.

    \item Finally, we made minor revisions addressing: differences between the
    Barker function vs. the original MH test, and sampling with vs. without
    replacement.
\end{enumerate}

We are confident that the current manuscript is of far better quality than the
NIPS submission, and we appreciate the efforts of the NIPS reviewers to give us
ideas for improvement.
